### 2016-09-28 rebuttal.tex

should this be
\begin{quote}
The measure parameter of the simplify function lets the user specify the Python function used to determine how
\end{quote}
\begin{solution}
We have changed the sentence as suggested.
\end{solution}
\question Section 4.1
Should mpmath be cited here?

\begin{solution}
We have added a citation for mpmath.
\end{solution}
\end{questions}

\section{Reviewer 3}

\begin{questions}
\question The paper introduces SymPy, a well-known pure Python library for
symbolic computation. It covers many aspects of the library: architecture,
basic usage, overview of modules, a more detailed look into some of them, and
physics application.

The writing style is mostly clear and easy to understand. Some example code is
provided to further explain the use of various module, classes, and functions.
Unfortunately, the paper is very unconnected and disorganized, with some
unnecessary repetition and some things left undefined. Further, parts of the
supplement should be moved to the main paper and vice versa. All of this makes
the paper look more like a collection of unconnected or, at best, very loosely
connected parts, instead of a meaningful whole.

Another big problem of the paper is the lack of aim. Some parts of SymPy are
covered at informative level (short descriptions of the elements related to
some subject), some at the beginners level (basic usage examples), while some
go deep in internal SymPy implementation of certain features. This structure
leaves the impression that different, yet mutually intermingled sections aim
at different audiences.

Moreover, these vastly differently approached elements come in no specific
order, and with no obvious reason why each of them is picked to be covered at
all and, specifically, at the chosen level of complexity in the approach.

I suggest a major rewrite of the paper, to improve the structure and group differently approached subjects. It would probably be best to:
\begin{enumerate}
\item Create a new section (following the introduction of SymPy) on projects that use SymPy, and put in it the materials currently available in supplement's sections 8, 9, 11. The comparison with Mathematica (supplement's section 10) should be moved either to the introduction as a section, or right after the introduction as its own section, but it should not be in the middle of the description of SymPy-powered projects.
\item  This should be followed by the list of SymPy packages and modules (currently section 3) and descriptions of selected modules (currently sections 3.1, 3.3, 3.5, supplement's sections 5, 7, and 9).
\item Now, basic usage can be given as its own section (currently done in sections 2.1 and 2.3), followed by introductions on usage of various modules (currently in sections 3.2, 3.4, 3.6, 4, 5, and supplement's sections 2, 3, 4, 6).
\item In-depth architecture (most of the so far unmentioned sections) can be given either as its own section, or made into a supplement of its own (as it is naturally far more technical and less interesting to general audience).
\item The current conclusion works fine as the finishing section of the paper.
\end{enumerate}
\begin{solution}
  We have made the following changes to the paper

### 2016-09-28 coverletter.tex
Add the sentence back in
It was removed in 59dcf547dfd813fe91a377c6ddcfda6462f66dbf.
Fix my office number
Remove confusing sentence from letter

\usepackage{hyperref}
% \signature{Aaron Meurer}
\address{Aaron Meurer \\
ERGS: \url{http://www.ergs.sc.edu/} \\
Nuclear Eng., Mechanical Eng. Dept. \\
University of South Carolina \\
541 Main Street, St. 011 \\
Columbia, SC 29201 \\
\url{asmeurer@gmail.com}}

@@

Reviewer 1 had concerns that the paper was out of scope, but the editor has
confirmed that it is in scope. Many of the points that reviewer 3 raised were
in regards to the relevance of various sections. The intended scope of this
paper was to be an architecture paper for SymPy's 1.0 release. We have
examined reviewer 3's points through this lens. In light of this, which
contents were previously in the supplement vs.\ the main manuscript may have
been confusing to a general audience. To address this, we have restructured
the manuscript to make the paper more readable to those not already experts in
SymPy or symbolic mathematics.

We thank you again for your consideration. Given these edits, we believe that
the manuscript is now suitable for publication in PeerJ Computer Science. If
there are further questions or concerns please do not hesitate to contact us.

>>>>

\usepackage{hyperref}
% \signature{Aaron Meurer}
\address{Aaron Meurer \\
ERGS: \url{http://www.ergs.sc.edu/} \\
Nuclear Eng., Mechanical Eng. Dept. \\
University of South Carolina \\
541 Main Street, St. 009 \\
Columbia, SC 29201 \\
\url{asmeurer@gmail.com}}

@@

Reviewer 1 had concerns that the paper was out of scope, but the editor has
confirmed that it is in scope. Many of the points that reviewer 3 raised were
in regards to the relevance of various sections. The intended scope of this
paper was to be an architecture paper for SymPy's 1.0 release. We have
examined reviewer 3's points through this lens. To address this, we have
restructured the manuscript to make the paper more readable to those not
already experts in SymPy or symbolic mathematics.

We thank you again for your consideration. Given these edits, the manuscript
has been greatly improved and we believe that it is now suitable for
publication in PeerJ Computer Science. If there are further questions or
concerns please do not hesitate to contact us.
